---
title: "Untitled"
output: html_document
date: "2026-03-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(tidyverse)
library(here)
library(tidyverse)
library(here)

polldata <- read.csv("https://mrp-psf.ams3.digitaloceanspaces.com/polls/winter_10k.csv")

polldata <- polldata %>%
  mutate(
    britishpride_numeric = case_when(
      britishpride == "Very proud"                    ~ 5,
      britishpride == "Quite proud"                   ~ 4,
      britishpride == "Neither proud nor ashamed"     ~ 3,
      britishpride == "Quite ashamed"                 ~ 2,
      britishpride == "Very ashamed"                  ~ 1,
      TRUE                                            ~ NA_real_
    )
  )

polldata_small <- polldata %>%
  select(britishpride, britishpride_numeric, region) %>%
  mutate(
    country = case_when(
      region %in% c("East Midlands", "East of England", "Greater London",
                    "North East England", "North West England", "South East England",
                    "South West England", "West Midlands", "Yorkshire and the Humber",
                    "London", "England") ~ "England",
      region == "Scotland" ~ "Scotland",
      region == "Wales"    ~ "Wales",
      TRUE                 ~ NA_character_
    )
  )



country_avg_poll_full <- polldata_small %>%
  filter(!is.na(country), !is.na(britishpride_numeric)) %>%
  count(country, britishpride_numeric) %>%
  group_by(country) %>%
  mutate(prop = n / sum(n) * 100) %>%
  ungroup() %>%
  select(country, britishpride_numeric, prop) %>%  # drop n before pivoting
  pivot_wider(names_from = britishpride_numeric, values_from = prop) %>%
  rename(very_ashamed = "1", quite_ashamed = "2", neither = "3",
         quite_proud = "4", very_proud = "5")





write.csv(country_avg_poll_full, here("output", "country_avg_poll_britishpride_full_revised.csv"), row.names = FALSE)

country_avg_poll <- country_avg_poll_full %>%
  mutate(net_score_poll_cntry_avg = very_proud + quite_proud - quite_ashamed - very_ashamed) %>%
  select(country, net_score_poll_cntry_avg)

write.csv(country_avg_poll, here("output", "country_avg_poll_britishpride_revised.csv"), row.names = FALSE)
print(country_avg_poll)