---
title: "Untitled"
output: html_document
date: "2026-02-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}

library(here)
library(tidyverse)

```

```{r}


polldata <- read.csv("https://mrp-psf.ams3.digitaloceanspaces.com/polls/winter_10k.csv")


polldata <- polldata %>%
  mutate(head_of_state_numeric = case_when(
    head_of_state == "Britain should have an elected politician, such as a President, as the head of state" ~ 0,
    head_of_state == "Britain should continue to have a monarch as the head of state" ~ 1,
    TRUE ~ NA_real_
  ))


polldata_small <- polldata %>% select(head_of_state, head_of_state_numeric, region)

polldata_small <- polldata_small %>%
  mutate(
    country = case_when(
      region %in% c("East Midlands", "East of England", "Greater London",
                    "North East England", "North West England", "South East England",
                    "South West England", "West Midlands", "Yorkshire and the Humber",
                    "London", "England") ~ "England",
      region == "Scotland" ~ "Scotland",
      region == "Wales" ~ "Wales",
      TRUE ~ NA_character_
    )
  )


country_avg_headstate <- polldata_small %>%
  filter(!is.na(country), !is.na(head_of_state_numeric)) %>%
  group_by(country) %>%
  summarise(avg_head_of_state = mean(head_of_state_numeric*100)) 
  


write.csv(country_avg_headstate, here("output", "country_avg_headstate.csv"), row.names = FALSE)
    




write.csv(country_avg_poll, here("output", "country_headstate.csv"), row.names = FALSE)