---
title: "Untitled"
output: html_document
date: "2026-02-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r}
library(here)
library(tidyverse)

echr <- read.csv(here("output", "preds_echr_final_full.csv"))


echr %>%
  filter(net_final >= 1 & net_final <= 10) %>%
  nrow()

echr %>%
    filter(net_final <= 0) %>%
  nrow()
  


# Average of top 150
top_150_avg <- echr %>% 
  arrange(desc(net_final)) %>% 
  slice(1:150) %>% 
  summarise(avg = mean(net_final))



top_150_avg <- echr %>% 
  arrange(desc(net_final)) %>% 
  slice(1:150) %>% 
  count(region_2)



bottom_150_avg <- echr %>% 
  arrange((net_final)) %>% 
  slice(1:150) %>% 
  count(region_2)

# Average of bottom 150
bottom_150_avg <- echr %>% 
  arrange(net_final) %>% 
  slice(1:150) %>% 
  summarise(avg = mean(net_final))

echr_region <- echr %>% 
  group_by(region_2) %>%
  summarise(net_final_region = mean(net_final))





# Most pro -echr 
most_pro_leave <- echr %>% slice_max(net_final, n = 1) %>% select(const_name, net_final)

#most anti echr 
most_anti_rmain <- echr %>% slice_min(net_final, n = 1) %>% select(const_name, net_final)

# Median constituency
median <- echr %>% slice_min(abs(net_final - median(net_final)), n = 1) %>% select(const_name, net_final)


