---
title: "Untitled"
output: html_document
date: "2026-02-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(here)
library(tidyverse)


```

```{r}
headstate <- read.csv(here("output", "preds_headstate_reweighted.csv"))

headstate_2 <- read.csv(here("output", "preds_headstate.csv"))

## group by country 

cntry_avg <- headstate_2 %>%
               group_by(region_2) %>% 
               summarise(avg_cntry_headstate = mean(headstate_score_reweighted)) %>%
               ungroup()


headstate %>% 
  arrange(headstate_score_reweighted) %>% 
  slice(1)




# Average of top 150
top_150_avg <- headstate %>% 
  arrange(desc(headstate_score_reweighted)) %>% 
  slice(1:150) %>% 
  summarise(avg = mean(headstate_score_reweighted))



## IQ range: 


top_150 <- headstate %>% 
  slice_max(order_by = headstate_score_reweighted, n = 150, with_ties = FALSE)

bottom_150 <- headstate %>% 
  slice_min(order_by = headstate_score_reweighted, n = 150, with_ties = FALSE)

top_150_mean <- top_150 %>% 
  summarise(mean_net_score = mean(headstate_score_reweighted, na.rm = TRUE))

bottom_150_mean <- bottom_150 %>% 
  summarise(mean_net_score = mean(headstate_score_reweighted, na.rm = TRUE))





iqr_lower <- quantile(headstate$headstate_score_reweighted, 0.25)
iqr_upper <- quantile(headstate$headstate_score_reweighted, 0.75)



top_150_avg <- headstate_2 %>% 
  arrange(desc(headstate_score_reweighted)) %>% 
  slice(1:150) %>% 
  count(region_2)



bottom_150_avg <- headstate_2 %>% 
  arrange((headstate_score_reweighted)) %>% 
  slice(1:150) %>% 
  count(region_2)

# Average of bottom 150
bottom_150_avg <- headstate %>% 
  arrange(headstate_score_reweighted) %>% 
  slice(1:150) %>% 
  summarise(avg = mean(headstate_score_reweighted))



### median, lowest, highest constiteuncy ## 




# Most left bias
most_monarchy <- headstate %>% slice_max(headstate_score_reweighted, n = 1) %>% select(const_name, headstate_score_reweighted)

#most right bias
most_republican <- headstate %>% slice_min(headstate_score_reweighted, n = 1) %>% select(const_name, headstate_score_reweighted)

# Median constituency
median <- headstate %>% slice_min(abs(headstate_score_reweighted - median(headstate_score_reweighted)), n = 1) %>% select(const_name, headstate_score_reweighted)


