---
title: "Nato Write up"
output: html_document
date: "2026-02-26"
---

```{r} setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE
```

```{r}

library(here)
library(tidyverse)

```

```{r}


nato <- read.csv(here("output", "preds_nato_reweighted_revised.csv"))






## group by country 

cntry_avg <- nato %>%
               group_by(region_2) %>% 
               summarise(avg_cntry_nato_net_rewegithed = mean(net_score_reweighted)) %>%
               ungroup()



# Average of top 150
top_150_avg <- nato %>% 
  arrange(desc(net_score_reweighted)) %>% 
  slice(1:150) %>% 
  summarise(avg = mean(net_score_reweighted))



top_150_avg <- nato %>% 
  arrange(desc(net_score_reweighted)) %>% 
  slice(1:150) %>% 
  count(region_2)



bottom_150_avg <- nato %>% 
  arrange((net_score_reweighted)) %>% 
  slice(1:150) %>% 
  count(region_2)

# Average of bottom 150
bottom_150_avg <- nato %>% 
  arrange(net_score_reweighted) %>% 
  slice(1:150) %>% 
  summarise(avg = mean(net_score_reweighted))


## number of seats less than 50 

less_50 <- nato %>%
  filter(net_score_reweighted < 50) %>%
  select(const_name, net_score_reweighted) %>%
  arrange(net_score_reweighted)



low_10 <- nato %>%
  arrange(net_score_reweighted) %>%
  slice(1:10) %>%
  select(const_name,net_score_reweighted)






# Most pro-NATO
most_nato <- nato %>% slice_max(net_score_reweighted, n = 1) %>% select(const_name, net_score_reweighted)

#most right bias
least_nato <- nato %>% slice_min(net_score_reweighted, n = 1) %>% select(const_name, net_score_reweighted)

# Median constituency
median <- nato %>% slice_min(abs(net_score_reweighted - median(net_score_reweighted)), n = 1) %>% select(const_name, net_score_reweighted)


