---
title: "Untitled"
output: html_document
date: "2026-02-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}

library(here)
library(tidyverse)

```

```{r}






polldata <- read.csv("https://mrp-psf.ams3.digitaloceanspaces.com/polls/winter_10k.csv")



polldata <- polldata %>%
  mutate(
    nato_rl = case_when(
      nato == "The UK should remain a member of NATO" ~ 1,
      nato == "The UK should leave NATO"              ~ 0,
      TRUE                                            ~ NA_real_   
    )
  )


polldata_small <- polldata %>%
  select(nato, nato_rl, region) %>%
  mutate(
    country = case_when(
      region %in% c(
        "East Midlands", "East of England", "Greater London",
        "North East England", "North West England", "South East England",
        "South West England", "West Midlands", "Yorkshire and the Humber",
        "London", "England"
      ) ~ "England",
      region == "Scotland" ~ "Scotland",
      region == "Wales"    ~ "Wales",
      TRUE                 ~ NA_character_
    )
  )

# Country averages

country_avg_nato <- polldata_small %>%
  filter(!is.na(country)) %>%                
  group_by(country) %>%
  summarise(
    n_total   = n(),
    n_remain  = sum(nato == "The UK should remain a member of NATO", na.rm = TRUE),
    n_leave   = sum(nato == "The UK should leave NATO", na.rm = TRUE),
    n_dk      = sum(nato == "Don’t know", na.rm = TRUE)
  ) %>%
  mutate(
    remain_na  = n_remain / n_total * 100,
    leave_nato = n_leave  / n_total * 100,
    dont_know  = n_dk     / n_total * 100,
    net_score  = remain_na - leave_nato    
  )





write.csv(country_avg_nato, here("output", "country_poll_nato.csv"), row.names = FALSE)









