---
title: "Untitled"
output: html_document
date: "2026-03-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
riots_1 <-  read.csv(here("output", "preds_riotslikely_reweighted.csv"))





riots_2 <- riots_1 %>%
  mutate(
     likely = very_likely + quite_likely,
    unlikely = very_unlikely + quite_unlikely
  ) %>%
  select(const_name, likely, unlikely, neither, net_score_reweighted)


```
## proprotion who say poud  

summary(riots_2$likely) ## 72 % 

## ashamed  ## 

summary(riots_2$unlikely) ## 9 %

 

summary(bbc_2$dont_know) #20




## vey proud v somwaht proude - 



```


##

negative_net <- brit_pride_1 %>%
  filter(net_score_reweighted < 0) %>%
  select(const_name, net_score_reweighted) %>%
  arrange(net_score_reweighted)

## No constineuncies where think has right wing bias 

nrow(negative_net)
negative_net


greater_40 <- brit_pride_1 %>% 
  filter(net_score_reweighted >= 40) %>%
  select(const_name, net_score_reweighted) %>%
  arrange(net_score_reweighted)

### 244 constituneices where left > right by 40 or more 


nrow(negative_net)
negative_net


region_likely <- riots_1 %>% group_by(region_2) %>%
  summarise(region_avg = mean(net_score_reweighted)) 



## England 68 
## Scotland 71
## Wales 71



greater_50 <- riots_1 %>%
  filter(net_score_reweighted >= 50) %>%
  select(const_name, net_score_reweighted) %>%
  arrange(net_score_reweighted)





top_150 <- bbc_1 %>% 
  slice_max(order_by = net_score_reweighted, n = 150, with_ties = FALSE)

bottom_150 <- bbc_1 %>% 
  slice_min(order_by = net_score_reweighted, n = 150, with_ties = FALSE)

top_150_mean <- top_150 %>% 
  summarise(mean_net_score = mean(net_score_reweighted, na.rm = TRUE))

bottom_150_mean <- bottom_150 %>% 
  summarise(mean_net_score = mean(net_score_reweighted, na.rm = TRUE))





# Most proud
most_likely <- riots_1 %>% slice_max(net_score_reweighted, n = 1) %>% select(const_name, net_score_reweighted)

#most ashamed
most_unlikley <- riots_1 %>% slice_min(net_score_reweighted, n = 1) %>% select(const_name, net_score_reweighted)

# Median constituency
median <- riots_1 %>% slice_min(abs(net_score_reweighted - median(net_score_reweighted)), n = 1) %>% select(const_name, net_score_reweighted)



iqr_lower <- quantile(riots_1$net_score_reweighted, 0.25)
iqr_upper <- quantile(riots_1$net_score_reweighted, 0.75)

iqr_lower











