---
title: ''
output: html_document
date: "2026-03-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}


library(here)
library(tidyverse)


 gbnews_1 <-  read.csv(here("output", "preds_gbnews_reweighted.csv"))
 
 
 
 
 
 gbnews_2 <- gbnews_1%>%
  mutate(
    left_rw  = very_left + mod_left,
    right_rw = very_right + mod_right
  ) %>%
  select(const_name, left_rw, right_rw, no_bias, dont_know, net_score_reweighted)


 ```
 ## proprotion who say left- bias 
 
 summary(gbnews_2$left_rw) ## 9 % 
 
## no bias ## 
 
 summary(gbnews_2$no_bias) ## 19
 
 
 summary(gbnews_2$right_rw)  ##40 
 
 summary(gbnews_2$dont_know) #32
 
 

 
 ## vey left v moderate left - 
 
 summary(gbnews_1$very_right) -# 22 %
 summary(gbnews_1$mod_right)  ## 18%
 
 
 ```
 
 
 ##
 
right_bias <- gbnews_1 %>%
  select(const_name, net_score_reweighted) %>%
    filter(net_score_reweighted > 0) %>%
  arrange(net_score_reweighted)
## every  ocnstitsutnecy think has right bias  
 

greater_30 <- gbnews_1 %>% 
    filter(net_score_reweighted >= 30) %>%
  select(const_name, net_score_reweighted) %>%
  arrange(net_score_reweighted)

### 46 constituneices where left > right by 30 or more 


nrow(negative_net)
negative_net


gbnews_region <- gbnews %>% group_by(region_2) %>%
  summarise(region_avg = mean(net_score_reweighted)) 

## england - 32% 
## scotland 35% 
## wales 35%



top_150 <- gbnews_1 %>% 
  slice_max(order_by = net_score_reweighted, n = 150, with_ties = FALSE)

bottom_150 <- gbnews_1 %>% 
  slice_min(order_by = net_score_reweighted, n = 150, with_ties = FALSE)

top_150_mean <- top_150 %>% 
  summarise(mean_net_score = mean(net_score_reweighted, na.rm = TRUE))

bottom_150_mean <- bottom_150 %>% 
  summarise(mean_net_score = mean(net_score_reweighted, na.rm = TRUE))



dontknow <- gbnews_1 %>% 
  

# Most left bias
most_left <- gbnews_1 %>% slice_min(net_score_reweighted, n = 1) %>% select(const_name, net_score_reweighted)

#most right bias
most_right <- gbnews_1%>% slice_max(net_score_reweighted, n = 1) %>% select(const_name, net_score_reweighted)

# Median constituency
median <- gbnews_1 %>% slice_min(abs(net_score_reweighted - median(net_score_reweighted)), n = 1) %>% select(const_name, net_score_reweighted)



iqr_lower <- quantile(gbnews_1$net_score_reweighted, 0.25)
iqr_upper <- quantile(gbnews_1$net_score_reweighted, 0.75)

iqr_lower



dontknow_25 <- gbnews_1 %>%
  filter(dont_know >= 25) %>%
  select(const_name, dont_know) %>%
  arrange(dont_know)


